---
title:  "Full Name of the Article"
subtitle: "Supplemental Material: Quantitative Anlaysis"
author: "Name - Remove for Blind Submission"
date:   "Compiled: `r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    toc: FALSE
    latex_engine: xelatex 
    keep_tex: true
geometry: "left=1.5in,right=1in,top=1in,bottom=1in"
bibliography: packages.bib 
csl: apa7.csl
nocite: '@*'
header-includes:
   - \usepackage{floatrow}
   - \usepackage{booktabs}
   - \usepackage{siunitx}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{colortbl}
   - \usepackage{array}
   - \usepackage{caption}
   - \usepackage{setspace}
   - \usepackage{fancyhdr}
---


\pagenumbering{arabic}
\setcounter{page}{1}
\fancypagestyle{plain}{%
\renewcommand{\headrulewidth}{0pt}%
\fancyhf{}%
\fancyhead[R]{\thepage}
\setlength\voffset{0.25in}
}
\pagestyle{plain}



\setcounter{figure}{0}
\setcounter{table}{0}
\captionsetup{labelfont=bf, 
textfont={it}, 
labelsep=newline,
justification=raggedright, 
singlelinecheck=false}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}
\renewcommand{\thefigure}{S.\arabic{figure}}
\renewcommand{\thetable}{S.\arabic{table}}



\clearpage
\setcounter{tocdepth}{3}
\tableofcontents    
\clearpage
\listoftables
\clearpage
\listoffigures
\clearpage


```{r, include=FALSE}
knitr::opts_chunk$set(comment     = "",
                      echo        = TRUE,
                      warning     = FALSE, 
                      message     = FALSE,
                      ft.align    ="left",
                      fig.pos     = "hb",     
                      fig.align   = "left",   
                      fig.width   = 5,     
                      fig.height  = 3)  
```


# BACKGROUND

* Be brief
* Use lists and bullets
* Do not need to include the entire manuscript

## Research Questions

Why?

## Sample

Who/when/where?


## Measures

What?


## Analysis

How?



\clearpage

# PREPARATION

## Load Packages

> From GitHub: this only needs to be done ONCE per computer installation

```{r, eval=FALSE}
library(devtools)
devtools::install_github("SarBearSchwartz/apaSupp")
```

> From CRAN

* This is a general list you might start with
* Make sure to edit this code chunk to delete packages you didn't end up using before finalizing
* ONLY put `library()` function calls here, do NOT add them in the lower part of the document!

```{r, results='hide', message=FALSE, error=FALSE, warning=FALSE}
library(apaSupp)
library(tidyverse)
library(readxl)
library(haven)
library(furniture)
library(rstatix)
library(ggpubr)
library(MOTE)
library(flextable)
library(texreg)
library(texreghelpr)
library(afex)
library(emmeans)
library(interactions)
library(performance)
```




> Global Settings 



```{r}
options(dplyr.summarise.inform = FALSE)

flextable::set_flextable_defaults(theme_fun = "theme_apa",
                                  font.size = 10,
                                  layout = "autofit")

ggplot2::theme_set(theme_bw())
```




\clearpage

## Load Data

> You can load Multiple files

* I suggest doing as much data cleaning in a separate "prep" file first
* Are these files publicly available (Open Science Framework)?

* Avoid printing the entire dataset
* Instead use
    + `tibble::glimpse()`
    + `head` or `psych::headTail()` with `apaSupp::apaTab()`

\clearpage


# DATA WRANGLING

> If this is a large task, I suggest seperating it into a seperate Rmd file and save the polished data file that is ready to go. 

Possible tasks may include...

* Factors
    + Declare so they aren't treated as continuous values
    + Apply value labels (text for output, tables, figures)
    + Arrange "reference" category to be first in order
* Deal with missing values
    + This is more often an SPSS issue
* Score any measures
    + Do any of the items need to be reverse coded
    + Aggregate "Sum" or "Mean" for subscores/domains or total/global
* Pivot Formats
    + Wide: one line per person
    + Long: one line per observation
    + Can have other formats




\clearpage

# EXPLORATORY DATA ANLAYSIS

## Sample Size

* Inclusion & Exclusion Criteria?
* Levels of sampling?


\clearpage

## Missing Data

* Which variables?
* How much?
* Patterns of missingness

Useful package: `naniar`


\clearpage

## Descriptive Summary

* min-max
* Means
* standard deviations
* Correlations

Common tools

* `summary()` - very basic, try to avoid
* `psych::describle()` - only for continuous variables
* `furniture::table1()` - basic descriptions, may compare groups
* `furniture::tableC()`
* `flextable::flextable()` with `apaSupp::theme_apa()` - generic for making any data frame into a table



\clearpage

## Varaible Distibutions

* 1 Categorical: `geom_bar()` or `geom_col()`
* 1 Continuous:  `geom_histogram()`
* 2 categorical: `geom_point()` or `geom_count()`






\clearpage

# ANALYSIS

Create sections dependent on project





\clearpage

# SESSION INFORMATION

```{r}
sessionInfo()
```


\clearpage

# BIBLIOGRAPHY

\doublespacing




```{r, echo=FALSE, results='hide'}
# Include the R programing language
toBibtex(citation())  

# Include specific packages
# toBibtex(citation("geepack"))

# write all citations to .bib file
knitr::write_bib(c(.packages()), "packages.bib") 
```




